Ontology Matching Paper An ontology alignment over Amsterdam (Parking spots, events and activities)

### 2016-05-08 milestone3/paper/paper.tex
done done done done done done dooooone

\begin{abstract}
The abstract should summarize the contents of the paper and should
contain at least 70 and at most 150 words. It should be written using the
\emph{abstract} environment.
\end{abstract}

>>>>

\begin{abstract}
	In this paper we build on the Ontology for Handicap Parking Spots and tackle the problem of ontology matching with same domain datasets. We research state of the art methods for ontology alignment and apply them to own and three other candidate ontologies.
	We observe that for finding equivalence some matchings are straightforward while others require great amount of human interference for selecting the appropriate matching algorithm. 
	We present the results for matching and aligning the ontologies, and discuss the findings placing them in the wider picture of Ontology matching for the Semantic Web.
\end{abstract}
